### 2019-05-16 doc/bilevel/paper.tex
Updated first section to include pessmistic bilevel

In multilevel optimization problems, a subset of decision variables
at each level is constrained to take values associated with an
optimal solution of a distinct, lower level optimization problem.
For example, a general formulation for bilevel programs is
\begin{equation}
\label{eqn:bilevel}
\begin{array}{ll}
\min_{x \in X, y \in Y}   & F(x,y)\\
\st                 & G(x,y) \leq 0\\
                    & y \in P(x)
\end{array}
\end{equation}
where
\[
\begin{array}{llll}
P(x) & = & \argmin_{y \in Y}    & f(x,y)\\
 & &                            & g(x,y) \leq 0
\end{array}
\]
$P(x)$ defines a \textit{lower-level problem}, which may have multiple solutions.
Here $x$ is the primary upper-level decision, and $y$ is the anticipated lower-level 
decision.

@@

\textbf{TODO: Describe pessimistic problems here.}

>>>>

In multilevel optimization problems, a subset of decision variables
at each level is constrained to take values associated with an
optimal solution of a distinct, lower level optimization problem.
For example, a general formulation for bilevel programs is
\begin{equation}
\label{eqn:bilevel}
\begin{array}{ll}
\min_{x \in X, y \in Y}   & F(x,y)\\
\st                 & G(x,y) \leq 0\\
                    & y \in P(x)
\end{array}
\end{equation}
where
\[
\begin{array}{llll}
P(x) & = & \argmin_{y \in Y}    & f(x,y)\\
 & &                            & g(x,y) \leq 0.
\end{array}
\]
$P(x)$ defines a \textit{lower-level problem}, which may have multiple solutions.
Here $x$ is the primary upper-level decision, and $y$ is the anticipated lower-level 
decision.

@@

Alternatively, a \textit{pessimistic} bilevel problem is when \eqref{eqn:bilevel} is expressed as

\begin{equation}
\label{eqn:bilevel_pess}
\begin{array}{ll}
\min_{x \in X, y \in Y}   & F(x,y)\\
\st                 & G(x,y) \leq 0\\
                    & \forall y \in P(x)
\end{array}
\end{equation}
where 
\[
\begin{array}{llll}
P(x) & = & \argmin_{y \in Y}    & f(x,y)\\
 & &                            & g(x,y) \leq 0.
\end{array}
\]
This formulation ensures that the selection value for $y$ will in fact maximize $F(x,y)$; in other words, the upper-level problem must be feasible for all values $y$ including the least favorable outcome of the lower-level problem $P(x)$. Unless otherwise stated, the canonical bilevel problem in the subsequent examples will be derived from the \textit{optimistic} approach presented in \eqref{eqn:bilevel}.
